---
output: 
  md_document:
    variant: gfm
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, collapse = TRUE)
```

# QcDM: **Q**uality **c**are for **D**iabetes **M**ellitus

## Overview

QcDM is an R package developed for generating glucometrics measures from
point-of-care blood glucose data at three different units of analysis:
patient-sample, patient-day, and patient-stay.

This package is a part of the 
[QcDM Project](https://github.com/nyilin/QcDM_Project.git), 
which provides a user-friendly R-Shiny user interface for convenient and 
flexible data processing, and generates a detailed and well-formatted report on 
the glucometrics measurements.

Users are strongly recommended to use QcDM via the R-Shiny interface. Sections
below describes the installation of the package and its basic usage.

## Installation

Package devtools is needed to install the QcDM package from Github:

```{r, eval=FALSE}
# First, install devtools if it is not already installed:
install.packages("devtools")
# Then, load devtools to install QcDM from Github:
library(devtools)
install_github("nyilin/QcDM")
```

## Basic usage

The QcDM package includes a simulated example data to illustrate its basic
usage, which was generated for 10 hypothetical ward locations (indicated by
letters A to J) in July 2020. The following is a preview of the first 5 rows of
the example data:

```{r}
library(QcDM)
data("gluDat")
```

The unit of measurement of glucose readings in the example data is mmol/L.

Before generating glucometrics measurements, first process the date-time stamps
of glucose readings, and identify glucose monitoring episodes based on the
admission information in `ADMISSION.ID`. In this example, we focus on ward A.

```{r}
gluDat2 <- FormatDate(dat = gluDat[gluDat$LOCATION == "A", ], yy = 2020, mm = 7)
gluDat3 <- GenEpisode(dat = gluDat2, epiMethod = "Admininfo")
```

Then, generate basic glucometrics measurements using the following cutoffs as an
example:

- Hyperglycemia: consider three cutoff values, i.e., higher than or equal to 14
mmol/L, 20 mmol/L or 24 mmol/L.
- Hypoglycemia: consider three cutoff values, i.e., below 4 mmol/L, 3 mmol/L or 
2.5 mmol/L.
- Normal range of glucose readings: above or equal to 4 mmol/L and below 10 mmol/L.
- Hyperglycemia index (HGI): above 10 mmol/L per hour of hospital stay.

```{r}
metricList <- GenGluM(dat = gluDat3, hypocutoffs = c(4, 3, 2.5),
                      hypercutoffs = c(14, 20, 24), normalrange = c(4, 10),
                      hgicutoff = 10, unitVal = 1)
knitr::kable(ProGluTable(metricList = metricList, unitVal = 1)[[1]])
```
